%Projects

\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\href{https://jaychen.app}{\underline{Portfolio}}} $|$ \emph{Next.js, React, JavaScript, Vercel, HTML, CSS, Git}}{}
    \resumeItemListStart
    \resumeItem{Built with Next.js, deployed to Vercel, has dark mode, and fetches real-time GitHub stats.}
    \resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://github.com/jundachen10/jays_resume}{\underline{This Resume}}} $|$ \emph{Github Actions, LaTex}}{}
    \resumeItemListStart
    \resumeItem{Wrote this resume in LaTex and deployed to GitHub.}
    \resumeItem{Built a custom GitHub Actions Yaml automation that deploys a PDF on push.}
    \resumeItemListEnd
    
\resumeProjectHeading
{\textbf{\href{https://github.com/jundachen10/buzzfeed}{\underline{Buzzfeed}}} $|$ \emph{C\#, SQL, DBeaver}}{}
    \resumeItemListStart
    \resumeItem{Developed a C\# and SQL program allowing users to create, save, and take quizzes stored in an MS SQL Server database.}
    \resumeItemListEnd


\resumeProjectHeading
{\textbf{\href{https://github.com/jundachen10/iMessage-css-practice}{\underline{iMessage Chat}}} $|$ \emph{HTML, CSS, SVG, Design}}{}
\resumeItemListStart
\resumeItem{Designed a copy of Apple's chat app to practice HTML/CSS design.}
\resumeItem{Embedded XML content within an SVG which allows it to display non-SVG content within its viewport.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{{\underline{Game Launcher}}} $|$ \emph{.NET Framework, SignalR, WPF, XAML}}{}
\resumeItemListStart
\resumeItem{Video game launcher for a video game arcade. Currently building in the .NET environment using WPF, and SignalR.}
\resumeItem{Communicates in real time between desktop and web clients with SignalR Hub.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{{\underline{Startup Venture}}} $|$ \emph{Go, Docker}}{}
\resumeItemListStart
\resumeItem{Startup venture with an experienced engineer. Currently learning about our tech stack: Go, Redis, Docker, Vultr, Terraform, mongoDB, and GraphQL.}
\resumeItem{Docker composed virtual proxy services hosted on Vultr Terraform.}
\resumeItem{Built a custom Cobra command CLI app using Go.}
\resumeItemListEnd



\resumeSubHeadingListEnd