% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
%\resumeSubheading

\section{Experience}

\resumeSubHeadingListStart

%
\resumeSubheading
{IT Business Analyst}{March 2024 - Present}
{Highmark Health enGen}{Pittsburgh, PA}
\resumeItemListStart
\resumeItem{Translated complex business requirements into actionable user stories across 15 scrum teams.}
\resumeItem{Enhanced our flagship product's user experience that direclty improved our 7 million members health outcomes; \textbf{93\% membership retention}.}
\resumeItem{Chosen as 1 of 9 for a rotation program; gained practical experience across a \$22B revenue area.}
\resumeItem{Spearheaded 200+ person monthly AI adoption talks; engaged with and influenced diverse stakeholders such as Project Managers,Developers, and leadership across the parent and subsidiary companies.}
\resumeItemListEnd
%
\resumeSubheading
{Professional Development}{June 2023 - March 2024}
{Academy Pittsburgh LLC}{Pittsburgh, PA}
\resumeItemListStart
\resumeItem{Completed 2 technical bootcamps in software development and business analysis to prepare for a career in product.}
\resumeItem{Performed business analyst training in collaboration with Apprenti and the Department of Labor for emerging professionals; 100\% recieved employment offer.}
\resumeItemListEnd
%
\resumeSubheading
{YouTube}{Nov 2021 -- June 2023}
{Creator}{Pittsburgh, PA}
\resumeItemListStart
\resumeItem{Grew channel to 100,000 subsribers in 4 years.}
\resumeItem{Followed the audience using impressions, click through, and google trends; \textbf{drove 22 million views in 2022}.}
\resumeItemListEnd
%
\resumeSubheading
{Customer Success Manager}{Mar 2019 -- Nov 2021}
{{\href{https://www.linkedin.com/company/gridwise}{\underline{Gridwise Mobile App}}}}{Pittsburgh, PA}
\resumeItemListStart
\resumeItem{Scaled from 15K to over \textbf{1 million users} using product and user retention strategies}
\resumeItem{Contributed to a \textbf{\$15.7M Series A funding} from investors including Louis Van Ahn and Severin Hacker, co-founders of Duolingo.}
\resumeItem{Partnered with sales and launched the first advertiser platform managing performance reviews; \textbf{grew ad revenue 10x from \$10,000 to \$100,000 monthly}.}
\resumeItem{Spearheaded the first Zendesk user support team, slashing response time 40\% with 98\% CSAT score.}
% \resumeItem{Conducted user interviews; produced 3 testimonial videos.}
\resumeItem{Doubled marketing ROI; used A/B tests and Mixpanel analytics.}
\resumeItem{Expanded product coverage 700\%; led 10 QA contractor team.}
% \resumeItem{Grew company YouTube to 3K subscribers; produced and starred in 60+ podcasts and videos to engage users.}
\resumeItemListEnd

% \resumeSubheading
% {Customer Success Manager}{Mar 2019 -- Nov 2021}
% {{\href{https://www.linkedin.com/company/gridwise}{\underline{Gridwise Mobile App}}}}{Pittsburgh, PA}
% \resumeItemListStart
% \resumeItem{Hybrid role at an early stage startup.}
% \resumeItem{Played a key role in securing \$20 million in Series A funding by enhancing user retention strategies.}
% \resumeItem{Supported by venture seed funding from Louis Van Ahn and Severin Hacker, co-founders of Duolingo.}
% \resumeItem{Built a Zendesk support system that cut response times by 40\% achieving a 98\% CSAT score.}
% \resumeItem{Executed marketing  to drive user growth from 15,000 to 1M+ MAU.}
% \resumeItem{Expanded coverage on a main product by 700\% by building a team of 10 QA contractors to support it.}
% \resumeItem{Launched a knowledge base by curating support articles, resulting in a monthly viewership of 3,000.}
% \resumeItem{Increased customer support productivity by 90\% by automating repeat tasks using Zendesk triggers and Zapier integrations.}
% \resumeItem{Introduced Zendesk systems that resolved 600 monthly tickets with a 98\% satisfaction rate.}
% \resumeItem{Launched the company YouTube channel to 3,000 subscribers in 1 year.}
% \resumeItem{Tripled Facebook group membership through use of A/B tests optimizing post performance and engagement.}
% \resumeItem{Improved marketing ROI by 200\% partnered with the VP of Marketing to identify top creatives using statistical methods like T-tests.}
% \resumeItem{Reduced B2B client churn by 20\% partnered with Director of Sales in improving click-through rates using Mixpanel and Everflow attribution.}
% \resumeItem{Developed content management calendars that resulted in a 2 season podcast and over 60 videos.}
% \resumeItem{Led on-site user interviews which resulted in 3 testimonial videos.}
% \resumeItem{Completed projects within an Agile framework across 30+ development sprints.}
% \resumeItemListEnd
%
\resumeSubheading
{Uber Driver}{Sept. 2016 -- Oct. 2018}
{Gig Worker}{Pittsburgh, PA}
\resumeItemListStart
\resumeItem{Drove for Uber gaining direct gig economy experience; \textbf{earned 1,100 5 star trips.}}
\resumeItem{Developed strategies for efficient time management and earnings optimization; \textbf{skills transferable to addressing Instacart shoppers' needs}.}
\resumeItemListEnd
%
\resumeSubheading
{Research Technician}{June 2010 -- Sept. 2016}
{University of Pittsburgh}{Pittsburgh, PA}
\resumeItemListStart
\resumeItem{\textbf{Co authored on 3 PubMed papers} by data driven medical research and the scientific method.}
\resumeItem{Selected as team of 3 specialists to procure liver cells for experimental transplant therapy in children with rare liver metabolic disorders.}

\resumeItemListEnd

\resumeSubHeadingListEnd